### 2016-10-26 sec-results.tex
Add results for ``low'' student group; incorporate some of Cheng's comments.

\section{Results}
To qualitatively evaluate our model, we can look at the latent state
representations we learn by fitting the model to some MOOC log data. We can
also inspect the transition matrix between the latent states discovered by
the model.

@@

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth,trim={0 3cm 0 2cm}]{figures/trans-comp/trans-avg.png}
    \caption{\label{fig:trans-avg}}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth,trim={0, 3cm 0 2cm}]{figures/trans-comp/trans-perfect.png}
    \caption{\label{fig:trans-perfect}}
  \end{subfigure}
  \caption{The latent state transition diagrams for a 4-state TL-HMM fit to
  \protect\textretrieval{} for all students (a) compared to only ``perfect''
  students (b).}
  \label{fig:trans-comp}
\end{figure*}

@@

>>>>

\section{Experiment Results}
As an analysis tool, the TL-HMM model provides with us the following two
patterns to characterize student behavior:
\begin{enumerate*}[label=(\arabic*)]
  \item latent state representations, and
  \item latent state transitions.
\end{enumerate*}
Thus to evaluate the proposed model, we conduct experiments to
qualitatively analyze both types of patterns discovered from empirical MOOC
log data.

@@

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.33\textwidth}
    \includegraphics[width=\textwidth,trim={0 3cm 0 2cm}]{figures/trans-comp/trans-avg.png}
    \caption{\label{fig:trans-avg}}
  \end{subfigure}%
  \begin{subfigure}[t]{0.33\textwidth}
    \includegraphics[width=\textwidth,trim={0, 3cm 0 2cm}]{figures/trans-comp/trans-perfect.png}
    \caption{\label{fig:trans-perfect}}
  \end{subfigure}%
  \begin{subfigure}[t]{0.33\textwidth}
    \includegraphics[width=\textwidth,trim={0, 3cm 0 2cm}]{figures/trans-comp/trans-low.png}
    \caption{\label{fig:trans-low}}
  \end{subfigure}
  \caption{The latent state transition diagrams for a 4-state TL-HMM fit to
  \protect\textretrieval{} for all students (a) compared to only ``perfect''
  students (b) and only ``low'' students (c).}
  \label{fig:trans-comp}
\end{figure*}

@@

In Figure~\ref{fig:trans-low} we plot the latent state transition diagram
for a second group of ``low'' students. These students were selected so
that they attempted all required quizzes in the course, but such that their
average quiz score was $\leq 70\%$. Here, we see that \emph{state 1} has a
large increase in size, where we might have expected state 3 to grow
instead.  However, there is an alternative explanation for this phenomenon:
Since state 1 seems to indicate a highly engaged student, it is a perfectly
reasonable explanation for the ``low'' student group as they are going to
be working hard to try to fill in the gaps in their knowledge. By contrast,
the ``perfect'' student group likely has many members who can take the quiz
more passively and get perfect marks, perhaps because they already know
much of the material being presented, or are just naturally strong and do
not require much background review to perform well. This also explains why
state 1 did not increase in size for the ``perfect'' group like we were
anticipating. Our model lends itself well to discovering this potentially
counter-intuitive insight directly from data.
